Clustering in a hyperbolic model of complex networks.

### 2019-02-21 proofs_finite_k.tex
revised sections 6 and 7

\begin{lemma} Let $\alpha>\frac12,\nu>0, k\geq 2$ be fixed and write $G_n := G(n;\alpha,\nu), G_{n,\text{Po}} := \GPo(n;\alpha,\nu)$.
Then

$$ c(k; G_n)-c(k; G_{n,\text{Po}}) \xrightarrow[n\to\infty]{\Pee} 0. $$
\end{lemma}

\begin{proof}
We use a sprinkling argument. 
We observe that $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu), G(n;\alpha,\nu)$ 
and $\GPo(n;\alpha,\nu)$ all live on the same disk (with radius $R = 2\ln \frac{n}{\nu}$).
We consider the coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
to the $(\alpha,R)$-quasi uniform distribution, the vertices of $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu)$
are $u_1,\dots, u_{(1+\epsilon)n}$; the vertices of $G(n;\alpha,\nu)$ are $u_1,\dots, u_n$ and 
the vertices of $\GPo(n;\alpha,\nu)$ are $u_1,\dots, u_N$ with $N\isd \Po(n)$ indepenent of
$u_1, u_2, \dots$.

@@

and simlarly for $\GPo$. In particular also 
$|c(k;G(n;\alpha,\nu)) - c(k;\GPo(n;\alpha,\nu))| > \sqrt{\eps} ) = O(\sqrt\eps)$.
Sending $\eps\searrow 0$ proves the lemma.
\end{proof}

@@

For all $\epsilon >0$, there is $H=H_\epsilon$ such that $\E N_1(H) \leq \epsilon n$.
\end{lemma}
\begin{proof}
By linearity of expectation and the probability mass of a centered disk,
\begin{align*}
\E N_1 = n \Pee(B_{R-H}(0)) \leq n e^{-\alpha H}
\end{align*}
Now, choose $H$ large enough such that $e^{-\alpha H} \leq \epsilon$.
\end{proof}
\begin{lemma}
Let $N_2(H)$ denote the number of vertices with no neighbour with height above $H \in [0,R]$ in the finite box model (with $n$ vertices).

For all $\epsilon >0$, there is $H=H_\epsilon$ such that $\E N_2 \leq \epsilon n$.
\end{lemma}
\begin{proof}
Let $\epsilon >0$. By Lemma~\ref{lem:n1}, there is $H_1$ such that the expected number of vertices with height at least $H_1$ is upper bounded by $\frac{\epsilon}{2}n$. So, if we write $N_{\geq H_1}$ for the number of vertices with height at least $H_1$ and $N_{\leq H_1}(H)$ for the number of vertices with height at most $H_1$ and no neighbour with height above $H$, then 
$$N_2(H) \leq N_{\geq H_1} + N_{\leq H_1}(H)$$
Let $\mu(H)$ denote the expected number of vertices in the neighbourhood ball above $H$ of a vertex with height $H_1$. For fixed $H_1$, $\mu(H)$ is a continuous function which is decreasing in $H$ and with $\mu(R)=0$. Therefore, there is $H_2$ large enough such that $1-e^{-\mu(H_2)} \leq \frac{\epsilon}{2}$. Hence,
$$\E N_{\leq H_1}(H_2) \leq n (1-e^{-\mu(H_2)}) \leq \frac{\epsilon}{2}$$
Finally, $\E N_2(H_2) \leq \E N_{\geq H_1} + \E N_{\leq H_1}(H_2) \leq \epsilon n$.
%For any vertex with height at most $H_1$, the probability mass of the neighbourhood ball $U_v$ of such a vertex $v$ above $H_1$ is upper bounded by $w(H_1)$.
%The expected number of points in $U_v$ is $\leq \epsilon n$.
% Write
%$$N_2 = \sum_{v = 1}^n \1_{\{v\text{ has no neighbour with rad. coord. }<R-H \}} $$
\end{proof}

\begin{lemma}
Let $c(k)$ denote the clustering function of the KPKVB random graph for $k \in \N$ and $c_{\leq H}(k)$ denote the average of the clustering coefficient of all vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$. Then,
$c(k) = c_{\leq H}(k) + O(\sqrt{\epsilon})$ with probability $\geq 1-O(\sqrt{\epsilon})+o(1)$.
\end{lemma}
\begin{proof}
Let $N(k)$ denote the number of vertices with degree $k$ in KPKVB.
Let $N_H(k)$ denote the number of vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$. From the previous two lemmas, it follows that $\E (n- N_H) \leq \epsilon n$ and from this also that $\E (N(k)-N_H(k))\leq \epsilon n$. Therefore, by Markov's inequality, 
$$\Pee( n-N_H \geq \sqrt{\epsilon}n) \leq \frac{\E (n-N_H)}{n} \leq \sqrt{\epsilon}$$
Consider 
$$c(k)-c_{\leq H}(k) = \frac{1}{N(k)}\sum c(v) - \frac{1}{N_H(k)}\sum c(v) \leq \frac{N(k)-N_H(k)}{N(k)}$$
So, finally
$$\Pee( c-c_{\leq H} = O(\sqrt{\epsilon}) ) \geq 1-O(\sqrt{\epsilon})$$
\end{proof}

@@

Let $\Delta_H(y)$ denote the probability that two neighbours of $(0,y)$ are adjacent. Let $\tau(y,k)$ be the Poisson probability that $(0,y)$ has degree $k$. Let $\rho(y)$ denote the truncated exponential density.

Then,
$c_{\leq H}(k) = (1+o(1))\int_0^H \int_0^H \int_0^H \Delta_H(y) \tau(y,k)\rho(y_1)\rho(y_2)\rho(y) dy_1dy_2 dy$ a.a.s.
\end{lemma}
\begin{proof}
First of all, as for $c_{\leq H}(k)$ all vertices involved have height $\leq H$, we can perform the computations in the box model: As $H$ is constant, for $R$ large enough, vertices with radial coordinates at least $R-H$ will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~30(ii) from the paper on the largest component of KPKVB, edges exist between such vertices in the disk if and only if they exist in the box.

@@

Let $M_{trig}(k,H)$ denote the number of tuples $(v,u,w)$ for pairwise distinct vertices $v,u,w$ such that $v,u,w$ form a triangle, the radial coordinates of $u,v,w$ are all at least $R-H$ and $v$ has degree $k$. Note that $N_{trig}(k,H) = \frac{1}{2}M_{trig}(k,H)$. $M_{trig}(k,H)$ can be written as a sum over $3$-tuples:
\begin{align*}
M_{trig}(k,H) = \sum_{(v,u,w) \in V_{\not =}^3} h(V,v,u,w)
\end{align*}
where $h$ is the indicator function that $v,u,w$ form a triangle, have radial coordinates at least $R-H$ and $v$ has degree $k$.
Using Mecke's formula, we obtain that 
\begin{align*}
\E M_{trig}(k,H) = \int_{E_R} \int_{E_R}\int_{E_R} \E h(V,v,u,w) dvdudw
\end{align*}
%Let $V \subset E_R$ denote the vertex set of the finite box model in the box $E_R = (-\frac{\pi}{2}e^{\frac{R}{2}},\frac{\pi}{2}e^{\frac{R}{2}}]\times (0,R]$.

@@

>>>>

\begin{lemma} Let $\alpha>\frac12,\nu>0, k\geq 2$ be fixed and write $G_n := G(n;\alpha,\nu), G_{n,\text{Po}} := \GPo(n;\alpha,\nu)$.
Then 
\[
	\left|c(k; G_n)-c(k; G_{n,\text{Po}})\right| \xrightarrow[n\to\infty]{\Pee} 0.
\]
\end{lemma}

\begin{proof}
We use a sprinkling argument. 
We observe that $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu), G(n;\alpha,\nu)$ 
and $\GPo(n;\alpha,\nu)$ all live on the same disk (with radius $R = 2\log\left(\frac{n}{\nu}\right)$).
We consider the coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
to the $(\alpha,R)$-quasi uniform distribution, the vertices of $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu)$
are $u_1,\dots, u_{(1+\epsilon)n}$; the vertices of $G(n;\alpha,\nu)$ are $u_1,\dots, u_n$ and 
the vertices of $\GPo(n;\alpha,\nu)$ are $u_1,\dots, u_N$ with $N\isd \Po(n)$ indepenent of
$u_1, u_2, \dots$.

@@

and simlarly for $\GPo$. In particular also 
$\Prob{|c(k;G(n;\alpha,\nu)) - c(k;\GPo(n;\alpha,\nu))| > \sqrt{\eps} } = O(\sqrt\eps)$.
Sending $\eps\searrow 0$ proves the lemma. \PvdH{I think we need to be a bit more precise here and set $\varepsilon = \varepsilon_n := Q n^{-1}$.
}
\end{proof}

@@

For all $\epsilon >0$, there is $H=H_\epsilon$ such that $\E N_1(H) \leq \epsilon n$.
\end{lemma}
\begin{proof}
By linearity of expectation and the probability mass of a centered disk,
\begin{align*}
\E N_1(H) = n \Pee(B_{R-H}(0)) \leq n e^{-\alpha H}
\end{align*}
Now, choose $H$ large enough such that $e^{-\alpha H} \leq \epsilon$.
\end{proof}
\begin{lemma}
Let $N_2(H)$ denote the number of vertices with no neighbour with height above $H \in [0,R]$ in the finite box model (with $n$ vertices).

For all $\epsilon >0$, there is $H=H_\epsilon$ such that $\E N_2 \leq \epsilon n$.
\end{lemma}
\begin{proof}
Let $\epsilon >0$. By Lemma~\ref{lem:n1}, there is $H_1$ such that the expected number of vertices with height at least $H_1$ is upper bounded by $\frac{\epsilon}{2}n$. So, if we write $N_{\geq H_1}$ for the number of vertices with height at least $H_1$ and $N_{\leq H_1}(H)$ for the number of vertices with height at most $H_1$ and no neighbour with height above $H$, then 
$$N_2(H) \leq N_{\geq H_1} + N_{\leq H_1}(H)$$
Let $\mu(H)$ denote the expected number of vertices in the neighbourhood ball above $H$ of a vertex with height $H_1$. For fixed $H_1$, $\mu(H)$ is a continuous function which is decreasing in $H$ and with $\mu(R)=0$. Therefore, there is $H_2$ large enough such that $1-e^{-\mu(H_2)} \leq \frac{\epsilon}{2}$. Hence,
$$\E N_{\leq H_1}(H_2) \leq n (1-e^{-\mu(H_2)}) \leq n \frac{\epsilon}{2}$$
Finally, $\E N_2(H_2) \leq \E N_{\geq H_1} + \E N_{\leq H_1}(H_2) \leq \epsilon n$.
%For any vertex with height at most $H_1$, the probability mass of the neighbourhood ball $U_v$ of such a vertex $v$ above $H_1$ is upper bounded by $w(H_1)$.
%The expected number of points in $U_v$ is $\leq \epsilon n$.
% Write
%$$N_2 = \sum_{v = 1}^n \1_{\{v\text{ has no neighbour with rad. coord. }<R-H \}} $$
\end{proof}

\begin{lemma}
Let $c(k)$ denote the clustering function of the KPKVB random graph for $k \in \N$ and $c_{\leq H}(k)$ denote the average of the clustering coefficient of all vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$. Then,
$c(k) = c_{\leq H}(k) + O(\sqrt{\epsilon})$ with probability $\geq 1-O(\sqrt{\epsilon})+o(1)$.
\end{lemma}
\begin{proof}
Let $N(k)$ denote the number of vertices with degree $k$ in KPKVB.
Let $N_H(k)$ denote the number of vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$. From the previous two lemmas, it follows that $\E (n- N_H) \leq \epsilon n$ and from this also that $\E (N(k)-N_H(k))\leq \epsilon n$. Therefore, by Markov's inequality, 
$$\Pee( n-N_H \geq \sqrt{\epsilon}n) \leq \frac{\E (n-N_H)}{n \sqrt{\epsilon}} \leq \sqrt{\epsilon}$$
Consider 
$$c(k)-c_{\leq H}(k) = \frac{1}{N(k)}\sum c(v) - \frac{1}{N_H(k)}\sum c(v) \leq \frac{N(k)-N_H(k)}{N(k)}$$
So, finally
$$\Pee( c-c_{\leq H} = O(\sqrt{\epsilon}) ) \geq 1-O(\sqrt{\epsilon})$$
\end{proof}

@@

Let $\Delta_H(y)$ denote the probability that two neighbours of $(0,y)$ are adjacent. Let $\tau(y,k)$ be the Poisson probability that $(0,y)$ has degree $k$. Let $\rho(y)$ denote the truncated exponential density.
\PvdH{These notations are not in sync with the rest of the paper.}
Then,
$c_{\leq H}(k) = (1+o(1))\int_0^H \int_0^H \int_0^H \Delta_H(y) \tau(y,k)\rho(y_1)\rho(y_2)\rho(y) dy_1dy_2 dy$ a.a.s.
\PvdH{I do not understand how a.a.s. is proven.}
\end{lemma}
\begin{proof}
First of all, as for $c_{\leq H}(k)$ all vertices involved have height $\leq H$, we can perform the computations in the box model: As $H$ is constant, for $R$ large enough, vertices with radial coordinates at least $R-H$ will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box.

@@

Let $M_{trig}(k,H)$ denote the number of tuples $(v,u,w)$ for pairwise distinct vertices $v,u,w$ such that $v,u,w$ form a triangle, the radial coordinates of $u,v,w$ are all at least $R-H$ and $v$ has degree $k$. Note that $N_{trig}(k,H) = \frac{1}{2}M_{trig}(k,H)$. $M_{trig}(k,H)$ can be written as a sum over $3$-tuples:
\begin{align*}
M_{trig}(k,H) = \sum_{(v,u,w) \in V_{\not =}^3} h(V,v,u,w)
\end{align*}
where $h$ is the indicator function that $v,u,w$ form a triangle, have radial coordinates at least $R-H$ and $v$ has degree $k$.
Using Mecke's formula, we obtain that 
\begin{align*}
\E M_{trig}(k,H) = \int_{E_R} \int_{E_R}\int_{E_R} \E h(V,v,u,w) dvdudw
\end{align*}
\PvdH{What is $E_R$ and what is $D_H$?}
%Let $V \subset E_R$ denote the vertex set of the finite box model in the box $E_R = (-\frac{\pi}{2}e^{\frac{R}{2}},\frac{\pi}{2}e^{\frac{R}{2}}]\times (0,R]$.

@@

\PvdH{Where is the proof of Theorem~\ref{thm:mainkfixed}?}

### 2019-02-21 proofs_infinite_k.tex
revised sections 6 and 7

Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$. To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of the clustering function $c^\ast(k;G)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.

\begin{proposition}[Transition to the infinite limit model]\label{prop:convergence_average_clustering_P_n}
As $n \to \infty$,
\[
	\left|\Exp{c^\ast(k_n; \Gbox)} - c(k_n;\Ginf)\right| = \smallO{s(k_n)}.
\]
\end{proposition}

@@

\begin{proof}[Proof of Theorem~\ref{thm:mainktoinfty}]
%By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
%\begin{align*}
%	&\hspace{-30pt}\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}\\
%	&\le \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{}c^\ast(k_n; \Gbox)\right|}}{C_{\alpha,\nu}\gamma(k_n)}
%		+ \frac{\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right|}{C_{\alpha,\nu}\gamma(k_n)}
%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| \\
%	&= \smallO{1}.
%\end{align*}
First of all, due to cancellation of equal terms we can rewrite
\begin{align*}
    c(k_n;G_n)-\gamma(k_n) =& c(k_n;G_n)-c^\ast(k_n;G_n)+c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)+c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox) \\
    &+c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)+\E c^\ast(k_n; \Gbox)-\gamma(k_n)
\end{align*}
Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
\begin{align*}
    \E[|c(k_n;G_n)-\gamma(k_n)|] \leq & \E[|c(k_n;G_n)-c^\ast(k_n;G_n)|]+\E[|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)|]\\&+\E[|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)|] 
    +\E[|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)|]\\&+\E[|\E c^\ast(k_n; \Gbox)-\gamma(k_n)|]
\end{align*}
At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c(k_n;\Ginf) = \gamma(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
\TM{ Maybe we can have a more clear reference? Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given. } \PvdH{I completely agree. I think that once the results for fixed $k$ have been included we can include a specific statement at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P} we can refer to.} All of this together yields that:
\begin{align*}
    \E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
\end{align*}
%\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point. }\PvdH{We can fix this by proving the scaling of $c_\infty(k)$ in Section~\ref{sec:asymptotics_average_clustering_ast_P}.}
i.e. the statement of the theorem.
%\[
%	\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}
%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| 
%	+ \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \gamma(k_n)\right|}}{C_{\alpha,\nu}\gamma(k_n)} = \smallO{1}.
%\]

>>>>

Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$. To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.

\begin{proposition}[Transition to the infinite limit model]\label{prop:convergence_average_clustering_P_n}
As $n \to \infty$,
\[
	\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right| = \smallO{s(k_n)}.
\]
\end{proposition}

@@

\begin{proof}[Proof of Theorem~\ref{thm:mainktoinfty}]
%By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
%\begin{align*}
%	&\hspace{-30pt}\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}\\
%	&\le \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{}c^\ast(k_n; \Gbox)\right|}}{C_{\alpha,\nu}\gamma(k_n)}
%		+ \frac{\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right|}{C_{\alpha,\nu}\gamma(k_n)}
%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| \\
%	&= \smallO{1}.
%\end{align*}
First of all, due to cancellation of equal terms we can rewrite
\begin{align*}
    c(k_n;G_n)-\gamma(k_n) =& c(k_n;G_n)-c^\ast(k_n;G_n)+c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)+c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox) \\
    &+c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)+\E c^\ast(k_n; \Gbox)-\gamma(k_n)
\end{align*}
Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
\begin{align*}
    \E[|c(k_n;G_n)-\gamma(k_n)|] \leq & \E[|c(k_n;G_n)-c^\ast(k_n;G_n)|]+\E[|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)|]\\&+\E[|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)|] 
    +\E[|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)|]\\&+\E[|\E c^\ast(k_n; \Gbox)-\gamma(k_n)|]
\end{align*}
At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model. 
%where we also used that $c(k_n;\Ginf) = \gamma(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
%\TM{ Maybe we can have a more clear reference? Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given. } \PvdH{I completely agree. I think that once the results for fixed $k$ have been included we can include a specific statement at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P} we can refer to.} 
All of this together yields that:
\begin{align*}
    \E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
\end{align*}
%\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point. }\PvdH{We can fix this by proving the scaling of $c_\infty(k)$ in Section~\ref{sec:asymptotics_average_clustering_ast_P}.}
i.e. the statement of the theorem.
%\[
%	\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}
%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| 
%	+ \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \gamma(k_n)\right|}}{C_{\alpha,\nu}\gamma(k_n)} = \smallO{1}.
%\]
